---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# sparr: Spatial and Spatiotemporal Relative Risk

The `sparr` package for R provides functions to estimate fixed and adaptive kernel-smoothed
spatial relative risk surfaces via the density-ratio method and perform subsequent inference.
Fixed-bandwidth spatiotemporal density and relative risk estimation is also supported.

## Installation

This package is available on CRAN, and we recommend installing it from there using the standard

```{r cran-installation, eval = FALSE}
install.packages('sparr')
```

If you wish to live on the bleeding edge, you may install from github using `devtools`:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github('tdavies/sparr')
```

## Example

This is a basic example of relative risk estimation for primary biliary cirrhosis cases
from north east England.

```{r pbc-example}
# Load library
library(sparr)

# Load data on casees of primary biliary cirrhosis from north east England
data(pbc)

# Split into cases and controls
pbc_case <- split(pbc)$case
pbc_cont <- split(pbc)$control

# Estimate global bandwidth for smoothing
h0 <- OS(pbc, nstar="geometric")

# Compute a symmetric (pooled) adaptive relative risk estimate
# with tolerance contours
pbc_rr <- risk(pbc_case, pbc_cont, h0=h0, adapt=TRUE, tolerate=TRUE,
               hp=OS(pbc)/2, pilot.symmetry="pooled", davies.baddeley=0.05)

# And produce a plot
plot(pbc_rr)
```
